Flexibility of interactions depends on habitat suitability

### 2019-08-22 paper/manuscript.Rmd
Little attempt of some formal results in the manuscript

We found that our models performe
We found that environmental suitability is an important variable

>>>>

We found that our models performed relativelly well. 
Overall we found no relationship between 
We found that environmental suitability is an important variable

```{r}
loadd(model_ranking)
waic_scores <- as.data.frame(model_ranking$waic) %>%
  tibble::rownames_to_column(var = "formula") %>%
  dplyr::select(formula, waic, se_waic)

loo_scores <- as.data.frame(model_ranking$loo) %>%
  tibble::rownames_to_column(var = "formula") %>%
  dplyr::select(formula, looic, se_looic)
```
